Generating the Blueprints of the Java Ecosystem

### 2015-03-29 msr2015-camera-ready.tex
almost there

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill January 11, 2007

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex,
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

@@

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

>>>>

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

\begin{abstract}
Examining a large number of software artifacts can provide
the research community with data regarding quality and design.
We present a dataset obtained by statically analyzing
22730 {\sc jar} files taken from the Maven
central archive, which is the de-facto application library
repository for the Java ecosystem. For our analysis
we used three popular static analysis tools
that calculate metrics regarding object-oriented design,
program size, and package design.
The dataset contains the metrics results that every tool
reports for every selected {\sc jar} of the
ecosystem. Our dataset can be used to produce interesting
research results, such as measure the domain-specific language usage.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\section{Introduction}
\label{sec:intro}

We present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java. All artifacts were taken from the {\it Maven Central Repository}~\cite{MAVEN}.

Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies, and the build order, Maven uses {\sc xml}. The central repository contains more than 400,000 {\sc jar}s, in a variety of programming languages such as Java, Clojure, Groovy, and Scala. All supported languages use the {\sc jvm} platform as their runtime environment. To build a software component, it dynamically downloads Java libraries and other plug-ins from the Maven central repository, and stores them in a local cache. The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.

To analyze the projects coming from Maven repository, we used the following tools: a) {\sc ckjm} \cite{Spi05g}, b) {\sc jd}epend~\cite{JDEPEND}, and c) {\sc clmt}~\cite{SGKL09}. All tools focus on three main aspects of a software system, namely: object-oriented design, program size, and package design. Such aspects are considered very important because they provide quantifiable information about the quality and structure of a software component.

In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for 22,730 {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.

\section{Dataset Construction Process}
\label{sec:data}

\begin{figure}
\centering
\includegraphics[scale=0.45]{import-process}
\caption{The dataset construction process.}
\label{fig:dataset-construction}
\end{figure}

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. In general, it follows the same methodology presented in reference \cite{MKLGS14}.

Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects that contain several versions. In our experiment, we only used Java projects. For every Java project all versions were filtered out and only the latest was kept. The process to identify them was the following; Every project consists of two {\sc jar} files, one that contains a compiled version of the project and one that contains the source code. The projects that did not had both binary and source {\sc jar}s, were excluded from the experiment. When the source {\sc jar} file was downloaded, it was scanned for Java source files. If the source files were present in the archive, then the project was flagged as a valid Java project.

When the selection process was finished, we created a series of processing tasks based on the selected {\sc jar}s, and added them to a task queue mechanism. Then we executed a number of workers that checked out tasks from the queue, applied the static analysis tools on each {\sc jar} and stored the results to the data repository (a {\sc m}y{\sc sql} database system). The workers were written in Python. In addition, there were several shell scripts (bash) that performed several checks and sanitisation tasks (e.g. checking for malformed results). The tools that were applied on every {\sc jar} were the following:

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g}; which calculates many software metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}. The version of the tool that we used for this experiment can be found in GitHub~\cite{CKJM}.

  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND}; a tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.

  \item \textbf{CLMT} \textit{(clmt)}~\cite{SGKL09}; which stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
\end{itemize}

\begin{table}
\centering
\caption{The selected Maven projects' size metrics.}
\label{tbl:oss-size-metrics}
\begin{tabular}{l r}
 \hline
\textbf{Metric} & \textbf{Value}\\
\hline
Project Count & 11,365\\
File Count & 449,213\\
Package Count & 59,436\\
Lines of Code & 74,565,772\\
Source Lines of Code & 40,921,287\\
Comment Lines of Code & 25,268,959\\
Number of Classes & 370,518\\
Number of Interfaces & 66,352\\
Number of Enumerations & 9,879\\
Measurement Count & 32,844,836\\
\hline
\end{tabular}
\end{table}

Table \ref{tbl:oss-size-metrics} presents several size metrics for our dataset. It includes 11,365 projects, with more than 74 million lines of code and almost 33 million unique measurements. Table~\ref{tbl:class-selected-metrics}, \ref{tbl:method-selected-metrics}, \ref{tbl:package-selected-metrics}, and \ref{tbl:size-selected-metrics} present the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics \cite{LOKI94}, \cite{CHKE94}, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics. Several metrics are calculated by more than one tool, like \textit{cyclomatic complexity} \cite{cabe76}, which is calculated by both \textit{clmt} and \textit{ckjm}. Both calculations are available in the database.

A series of newly introduced metrics were also stored in the database. Such metrics can count the usage of specific {\sc dsl} application libraries in a software project and they are included in the Table~\ref{tbl:size-selected-metrics}. The methodology to identify and calculate the {\sc dsl} metrics was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements (e.g. \textit{java.util.regex}). These statements indicated that the standard package that implements regular expressions was used, thus regular expressions were used in the project. Build files or other resources that may contain {\sc dsl}s were not included. One final assumption was also made; if {\sc xp}ath or {\sc xslt} were found in the source code, then the project would be marked as a project that utilizes {\sc xml}. This is because both languages are used for query and transformations on {\sc xml} {\sc dom} trees. Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries. Note that we focused on libraries that were included as part of the Java {\sc sdk}.

\begin{table}
\centering
\caption{List of selected {\sc dsl} application libraries.}
\label{tbl:dsl-list}
\begin{tabular}{l l}
 \hline
\textbf{DSL} & \textbf{Java Package}\\
\hline
Regular Expressions & \verb|java.util.regex|\\
XML & \verb|javax.xml|, \verb|org.w3c| and \verb|org.xml|\\
SQL & \verb|java.sql| and \verb|javax.sql|\\
XPath & \verb|java.xml.xpath|\\
XSLT & \verb|javax.xml.transform|\\
RTF & \verb|javax.swing.text.rtf|\\
HTML & \verb|javax.swing.text.html|\\
\hline
\end{tabular}
\end{table}

In Section~\ref{sec:dsl}, we describe an experiment based on these metrics. The experiment measures the popularity of {\sc dsl} usage for the dataset and therefore for the Java ecosystem in general.

\begin{table}
\centering
\caption{Class Design Metrics.}
\label{tbl:class-selected-metrics}
\begin{tabular}{l l}
\hline
Depth Of Inheritance Tree & \textit{ckjm}\\
Coupling Between Objects & \textit{ckjm}\\
Weighted Methods Per Class & \textit{ckjm}\\
Response For Class & \textit{ckjm}\\
Lack Of Cohesion In Methods & \textit{ckjm}\\
Number Of Children & \textit{ckjm}\\
Attribute Hiding Factor & \textit{clmt}\\
Coupling Between Methods & \textit{ckjm}\\
Average Method Complexity & \textit{ckjm}\\
Cohesion Among Methods of Class & \textit{ckjm}\\
Data Access Metric & \textit{ckjm, clmt}\\
Inheritance Coupling & \textit{ckjm}\\
Lack Of Cohesion In Methods3 & \textit{ckjm}\\
Measure Of Aggregation & \textit{ckjm}\\
Measure Of Functional Abstraction & \textit{ckjm}\\
Number of Attributes & \textit{clmt}\\
Method Hiding Factor & \textit{clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Method Design Metrics.}
\label{tbl:method-selected-metrics}
\begin{tabular}{l l}
\hline
Number of Method Parameters & \textit{clmt}\\
Number of Methods & \textit{clmt, ckjm}\\
McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Package Design Metrics.}
\label{tbl:package-selected-metrics}
\begin{tabular}{l l}
\hline
Number of Concrete Classes & \textit{jdep}\\
Afferent Couplings & \textit{jdep, ckjm}\\
Efferent Couplings & \textit{jdep, ckjm}\\
Instability & \textit{jdep}\\
Abstractness & \textit{jdep}\\
Distance Main Sequence & \textit{jdep}\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Program Size Metrics.}
\label{tbl:size-selected-metrics}
\begin{tabular}{l l}
 \hline
Number of Classes & \textit{clmt, ckjm, jdep}\\
Number of Enumerations & \textit{clmt, ckjm}\\
Number of Interfaces & \textit{clmt, ckjm}\\
Module Count & \textit{clmt, ckjm}\\
Comments Lines Of Code & \textit{clmt}\\
Lines Of Code & \textit{clmt, ckjm}\\
Source Lines Of Code & \textit{clmt}\\
Function Oriented Code & \textit{clmt}\\
DSL Usage Count & \textit{clmt}\\
RTF Usage Count & \textit{clmt}\\
Regex Usage Count & \textit{clmt}\\
HTML Usage Count & \textit{clmt}\\
XPath Usage Count & \textit{clmt}\\
XSLT Usage Count & \textit{clmt}\\
XML Usage Count & \textit{clmt}\\
SQL Usage Count & \textit{clmt}\\
File Count & \textit{clmt}\\
\hline
\end{tabular}
\end{table}

\section{Database Structure}
\label{sec:db}

Figure~\ref{fig:database-schema} illustrates the database schema. Specifically, it consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}. The central database table is \textit{measurement}, which holds the measurement values. The other tables can be used for normalization.

Metrics are divided into six categories that define their scope; \textit{module}, \textit{class}, \textit{method}, \textit{code unit}, and \textit{project-wide}. These values are stored in \textit{category} database table.

The descriptive names for each metric are stored in the \textit{measurement\_type} database table. There are 65 metrics available in the dataset. The names are composed by the actual metric name and the tool that was used to calculate them. For instance, \textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity generated by the \textit{clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the \textit{ckjm} tool.

Filenames, methods, classes and package names along with other identifiers are stored in the \textit{identifiers} table. Note that each measurement has a related filename and a related identifier that points to a software element. For example the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related to the identifier \textit{com.scalagent.jmx}.
Finally, the database table \textit{project} contains the related project identifiers, directly extracted from the maven repository.

\begin{figure*}
\centering
\includegraphics[scale=0.65]{database-schema}
\caption{The database schema.}
\label{fig:database-schema}
\end{figure*}

\section{Research Opportunities}
\label{sec:research-opportunities}

The measurements provided by our dataset, can be used by researchers and practitioners alike. Researchers can use the data to experiment with new software quality models, or validate them with real projects. Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools produce correct results.

The dataset also includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}. These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns~\cite{KARA14} as we illustrate in the following section.

Finally, our dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for metric correlations. This is because their datasets were also produced by analyzing projects coming from the Maven repository.

\section{Experimenting with the Dataset}
\label{sec:dsl}

\begin{table}
\centering
\caption{Top {\sc dsl} Usage Combinations.}
\label{tbl:dsl-top-usage}
\begin{tabular}{l r}
 \hline
\textbf{DSLs} & \textbf{Count}\\
\hline
XML & 1,561\\
Regex & 909\\
SQL & 493\\
XML, XSLT & 475\\
Regex, XML, XSLT & 158\\
Regex, XML & 303\\
SQL, XML & 162\\
Regex, SQL & 116\\
Regex, SQL, XML, XSLT & 80\\
Regex, SQL, XML & 71\\
SQL, XML, XSLT & 54\\
XML, XPath & 50\\
\hline
\end{tabular}
\end{table}

The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of {\sc dsl}s in multiple Java projects. The related metrics can be found in the database table named \textit{measuremnt\_type}, and they are the following: \textit{RTFUsage}, \textit{RegexUsage}, \textit{HTMLUsage}, \textit{HTMLUsage}, \textit{XPathUsage}, \textit{XSLTUsage}, \textit{XMLUsage}, \textit{SQLUsage}, and \textit{DSLCount}. A Python script that analysed the measurements stored in the database, we produced the results illustrated in Table~\ref{tbl:dsl-top-usage}. This table, lists popular {\sc dsl} usage combinations found in our dataset. An interesting observation is that {\sc xml} is the most widespread {\sc dsl} with 1,561 occurrences in 11,365 projects (13\%). Regular expressions are also popular with 909 occurrences (7\%). Note that the numbers represents the projects where {\sc xml} and regular expressions were used as the only {\sc dsl}.

\section{Limitations}
\label{sec:limit}

As we mentioned earlier, to produce our dataset we adopted a narrow selection process. In particular, we identified and analyzed only projects that were written in Java and had both the source code and the binary {\sc jar} available in the repository. The latter reduced significantly the number of projects that were analyzed, because many of them provided only the binary {\sc jar}. Since only \textit{clmt} analyses the source code, this resulted in the reduction of the number of measurements that exposed object-oriented and package design issues.

Finally, only one version was analyzed per project (the latest, unless it violated the aforementioned restriction).
This decision renders the dataset unusable, for research focused on software evolution.

\section{Related Work}
\label{sec:rel}

The Maven ecosystem has been previously analyzed by Raemaekers et al.~\cite{RDV13} to produce the {\it Maven dependency dataset}. Apart from basic information like individual methods, classes, packages and lines of code for every {\sc jar}, this dataset also includes a database with all the connections between the aforementioned elements.

Also, Mitropoulos et al. performed a similar experiment~\cite{MKLGS14}. In particular, they used the FindBugs~\cite{HP04} static analysis tool, to analyze a large part of the maven repository. Their dataset includes for each {\sc jar}, a corresponding bug collection produced by FindBugs. Our work differs from these two approaches since it presents the metrics calculated by the three different static analysis tools that calculate metrics regarding object-oriented design, program size, and package design.

\section{Conclusions}
\label{sec:conc}

We presented a dataset created by applying three different static analysis tools on Java projects coming from the Maven Central repository. The results invlove a variety of software metrics from program size to object-oriented design.
%In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates made in the repository.
We have also shown how our data can be used to extract meaningful results concerning {\sc dsl} usage in Java Projects.

As we discussed, our selection process was strict, filtering out projects that did not have the project's sources. However, we are planning to expand our project coverage in the future and include projects that cannot be analysed by all tools (due to source code unavailability).
Finally, by including all versions for each project we can allow researchers to use our dataset in the evolution context.

\section{Availability}

The dataset and the source code of this publication, along with some utility scripts are available at \url{https://github.com/bkarak/data_msr2015}. The {\sc sql} dump of the database is available at \url{http://gaijin.dmst.aueb.gr/~bkarak/data_msr2015.bz2}.

%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

@@

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
\bibliography{msr}

\end{document}
